### 2012-11-15 ASA2013/asa2013.tex
la2pdf commit - 2012:11:15	12:56:24	(Thu15.Nov)

\begin{abstract}
The Minimum Variance Distortionless Reponse (MVDR) beamformer has lately been applied to active sonar imaging. While displaying an ability to improve the image quality beyond the limits of conventional beamformers, it relies on the estimation and inversion of a spatial covariance matrix for each the image pixels. This may discourage its use, since robustification methods must be introduced to ensure numerical and statistical validity\todo{denne tror jeg vi kutter}, and the computational complexity is cubic with the number of channels, O($M^3$).

>>>>

\begin{abstract}
The MVDR adaptive beamformer has lately been shown to improve image quality in active sonar systems, but relies on the estimation and inversion of a spatial covariance for each image pixel. This translates to a computational complexity that is cubic with number of channels.
